### 2025-10-06 conteudo/background/linux.tex
fix points from defense

\section{The Linux Kernel}
Linus Torvalds released the initial version of the Linux kernel, a Unix-like operating system kernel, in 1991. It was initially released under a license of Torvalds' creation, but the Linux kernel was later relicensed under GNU General Public License version 2 (GPLv2) in 1992.
%
It began gaining popularity in the late
1990s~\citep{linuxbook}. Contrary to popular belief, Linux is not a
complete operating system, as it lacks components like filesystem utilities and
windowing systems. The so-called ``Linux distributions'' commonly
recognized by the public are GNU/Linux operating systems, which
include various essential applications alongside the Linux kernel,
such as system~\citep{gnuref}. Examples of Linux distributions are Ubuntu 
and Arch Linux.

>>>>

\section{The Linux Kernel}
Linus Torvalds released the initial version of the Linux kernel, a Unix-like operating system kernel, in 1991. It was initially released under a license of Torvalds' creation, but the Linux kernel was later relicensed under GNU General Public License version 2 (GPLv2) in 1992.
%
It began gaining popularity in the late
1990s~\citep{linuxbook}. Contrary to popular belief, Linux is not a
complete operating system, as it lacks components like filesystem utilities and
windowing systems. The so-called ``Linux distributions'' commonly
recognized by the public are GNU/Linux operating systems, which
include various essential applications alongside the Linux kernel,
such as core utilities, shelss, and compilers~\citep{gnuref}. Examples of Linux distributions are Ubuntu 
and Arch Linux.

### 2025-10-06 conteudo/results/eval.tex
fix points from defense

\section{Tool Results on BigCloneBench}

@@

>>>>

\subsection{Tool Results on BigCloneBench}

@@

\subsection{Performance Evaluation of the Tool}

Our performance evaluation, conducted on a machine equipped with a Ryzen 5700X processor 
and 32GB of RAM, highlights the efficiency of the tool's two-stage architecture. 
The offline Preprocessor step recorded a worst-case execution time of 8 minutes and 56 
seconds for the AMD Display driver and 9 minutes and 41 seconds for the IIO subsystem 
across five runs. ⏱️ In sharp contrast, the online Query Responder demonstrated real-time 
capabilities, processing user requests in under 2 seconds in all test cases. This significant 
performance difference underscores the effectiveness of separating the time-intensive 
analysis from the interactive querying phase.

### 2025-10-06 conteudo/results/participant.tex
fix some ~ before ref and cite and a wrong , on tool arch
fix points from defense

The experience of submitting a patch was not as we expected. The process took 7 
months and 16 days, significantly slower than expected. We initially submitted 
the patch on August 9, 2024, but we did not receive replies. Thus, we had to 
resend it on October 9, 2024. We received an initial response on November 3, 2024, 
requesting minimal changes. We submitted a second version with the requested 
changes on November 16, 2024. We did not receive replies initially and will 
need to resend the patch on February 7, 2025. We received a reply on 
February 11, 2025, asking for additional changes. We sent a third version on 
February 24, 2025, and the patch was accepted and integrated into the kernel 
codebase on February 25, 2025. Figure \ref{fig:timeline} illustrates the 
timeline of the patch submission.

@@

We discussed the Display driver with our point of contact at AMD to understand the 
reason for the slow patch submission process. We learned that some of the code in 
the driver is shared across all operating systems that support the implemented GPUs. 
This fact creates a complex process within AMD to format and submit changes across 
the supported systems while simultaneously implementing measures to mitigate errors. 
Additionally, we comprehended that AMD Display driver developers can not view 
duplicated code negatively, as we understand it is a good practice in software engineering. 
One example shared with us is that duplicated code enhances the independence of 
GPU driver code, allowing developers to make changes to a specific GPU without 
needing to test compatibility with others. This approach helps save a 
significant amount of time and effort.

>>>>

The experience of submitting a patch was not as we expected. The process took 7 
months and 16 days, significantly slower than expected. We initially submitted 
the patch on August 9, 2024, but we did not receive replies. Thus, we had to 
resend it on October 9, 2024. We received an initial response on November 3, 2024, 
requesting minimal changes. We submitted a second version with the requested 
changes on November 16, 2024. We did not receive replies initially and needed
to resend the patch on February 7, 2025. We received a reply on 
February 11, 2025, asking for additional changes. We sent a third version on 
February 24, 2025, and the patch was accepted and integrated into the kernel 
codebase on February 25, 2025. Figure~\ref{fig:timeline} illustrates the 
timeline of the patch submission.

@@

We discussed the Display driver with our point of contact at AMD to understand the 
reason for the slow patch submission process. We learned that some of the code in 
the driver is shared across all operating systems that support the implemented GPUs. 
This fact creates a complex process within AMD to format and submit changes across 
the supported systems while simultaneously implementing measures to mitigate errors. 
Additionally, we observed that AMD Display driver developers can not view 
duplicated code negatively, as we understand it is a good practice in software engineering. 
One example shared with us is that duplicated code enhances the independence of 
GPU driver code, allowing developers to make changes to a specific GPU without 
needing to test compatibility with others. This approach helps save a 
significant amount of time and effort.
